---
title: "An Overview of 'Practices of Coherence in Massive Twitch Chat'"
author: "Aspen Russell, Breanna E. Green"
date: "9/2/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Background


# Hypotheses
  1. Massive chat messages are shorter
  2. Massive chat messages contain less original content
  3. Massive chats contain fewer unique words

# Methods
 * Between April and August 2016 -- observed and recorded small & massive chats
 * Analyzed 50-message message segments -- 5 Smaller Chats vs 5 Massive Chats
 * Measured:
    + Scroll Rate
    + Message length
    + Amount fo original content -- as defined by John Sinclair's Theory of lexical Items
    + '# of unique voices in each segment

# Findings
  * H1: SUPPORTED
    + Shorthanding -- Massive chats contained fewer lexical items: Avg. 3 LIs per message vs 5.5 LIs in smaller chats
  * H2: SUPPORTED
    + Bricolage -- Massive chats included less unique content per 50-message segment: Avg. 85 unique LIs per segment vs 169 LIs in smaller chat
  * H3: UNSUPPORTED
    + Voice -- Total voice counts were comparable across

```{r installs, include=FALSE}
#install.packages("trackdown")
#library(trackdown)

#install.packages("devtools")
#devtools::install_github("Freguglia/rTwitchAPI")

library(rTwitchAPI)

```




```{r edit_env}
usethis::edit_r_environ()
```

```{r TwitchScrape}
# Setup authentication
twitch_auth()
#print(twitch_auth()) would show you this info! Bearer is included

# An example request to the streams endpoint
streams_live <- get_streams(first = 15, language = "en")
streams_live$data

#https://api.twitch.tv/v5/videos/<video_id>comments?content_offset_seconds=1000
```





```{r}
get_streams <- function(first=20,
                        after=NULL,
                        before=NULL,
                        community_id=NULL,
                        game_id=NULL,
                        language=NULL,
                        type=NULL,
                        user_id=NULL,
                        user_login=NULL){
  
  if(!provided_client_id()){}
  
  url <- 'https://api.twitch.tv/helix/streams'
  
  o <- GET(url,
           query = query_list(
             first=first,)) %>% content()
  
  if(!is.null(o$error) && o$error=="Unauthorized") stop(o$message)
  if(length(o$data)<1) stop("No results for this query parameters.")
  
  o$data <- o$data %>% transpose() %>% simplify_all() %>% dplyr::as_tibble()
  
  return(o)
}

```

```{r k}
#sock <- socketConnection(host = 'irc.chat.twitch.tv', port = 6667)
sock

```

