---
title: "An Overview of 'Practices of Coherence in Massive Twitch Chat'"
author: "Aspen Russell, Breanna E. Green"
date: "9/2/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Background


# Hypotheses
  1. Massive chat messages are shorter
  2. Massive chat messages contain less original content
  3. Massive chats contain fewer unique words

# Methods
 * Between April and August 2016 -- observed and recorded small & massive chats
 * Analyzed 50-message message segments -- 5 Smaller Chats vs 5 Massive Chats
 * Measured:
    + Scroll Rate
    + Message length
    + Amount fo original content -- as defined by John Sinclair's Theory of lexical Items
    + '# of unique voices in each segment

# Findings
  * H1: SUPPORTED
    + Shorthanding -- Massive chats contained fewer lexical items: Avg. 3 LIs per message vs 5.5 LIs in smaller chats
  * H2: SUPPORTED
    + Bricolage -- Massive chats included less unique content per 50-message segment: Avg. 85 unique LIs per segment vs 169 LIs in smaller chat
  * H3: UNSUPPORTED
    + Voice -- Total voice counts were comparable across

```{r installs, include=FALSE}
#install.packages("trackdown")
#library(trackdown)

#install.packages("devtools")
#devtools::install_github("Freguglia/rTwitchAPI")

library(rTwitchAPI)

```




```{r edit_env}
usethis::edit_r_environ()
```

```{r TwitchScarpe}
# Setup authentication
twitch_auth()

```

